A survey of HTTP caching options on the open Web

### 2015-01-05 sanity/paper1.tex
few details
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@934 43ef1190-90fd-4dd7-a769-d0121f02b80e
stub further work
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@935 43ef1190-90fd-4dd7-a769-d0121f02b80e
minor tweaks
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@936 43ef1190-90fd-4dd7-a769-d0121f02b80e

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness time or a promising feature. For
the former, this amounted to 22 servers, tabulated in~\todo{include
  table}. 70 servers always responded with promising features. As we
can see, apart from well-known Virtuoso and Callimachus servers, as
well as the Perl modules RDF::LinkedData and RDF::Endpoint, which is
partly developed by and runs on a server operated by this author, most
headers tells very little about the RDF-specific parts of the
underlying server implementation.

@@

Using the statistics system R\todo{ref}, we use a statistical test,
namely Pearson's $\chi^2$ test with simulated \pvalue (based on 10000
replicates). The simulation is done using a Monte Carlo method to
compensate for the fact that many servers will not expose caching
headers at all.

@@

@@

For endpoints, we made the following SPARQL query:
\begin{verbatim}
SELECT REDUCED ?Concept WHERE {[] a ?Concept} LIMIT 2
\end{verbatim}
which should be quite light, yet likely yield results.

@@

For endpoints, we examined the response message, to see if there are
any results to our query, and recorded that if there are.

>>>>

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness time or a promising feature. For
the former, this amounted to 22 servers, tabulated in~\todo{include
  table}. 70 servers always responded with promising features. As we
can see, apart from well-known Virtuoso and Callimachus servers, as
well as the Perl modules RDF::LinkedData and RDF::Endpoint, which is
partly developed by and runs on a server operated by this author, most
headers tells very little about the RDF-specific parts of the
underlying server implementation. A quick inspection of all
\httph{Server} headers confirm that few reveal any further detail.

@@

Using the statistics system R\todo{ref}, we use a statistical test,
namely Pearson's $\chi^2$ test with simulated \pvalue (based on 10000
replicates). The simulation is done using a Monte Carlo method to
compensate for the fact that many servers will not expose caching
headers at all, an issue that would otherwise violate the underlying
assumptions of the test.

@@

\section{Future work}

Identify implementations that expose suitable caching headers.

@@

For endpoints, we made the following SPARQL query:
\begin{verbatim}
SELECT DISTINCT ?Concept WHERE {[] a ?Concept} LIMIT 2
\end{verbatim}
which should be quite light, yet likely yield results.

@@

For endpoints, we examined the response message, to see if there are
any results to our query, and recorded that if there are. In addition
to the endpoints registered in the SPARQLES survey, our process found
18~endpoints that responded with results.
